\documentclass{ExpressiveCoverLetter}

\begin{document}

\coverletterheader[
    firstname=Tung,
    middleinitial=Anh,
    lastname=Nguyen,
    email=tung6100@uni.sydney.edu.au,
    phone=0410935365,
    % github=https://github.com/LeoTungAnh,
    city=Sydney,
    state=NSW,
]

\vspace{0.25in}
\today
\vspace{0.15in}


To whom it may concerns,

I am writing to express my interest in the Data Scientist or AI Engineer. With a PhD in Computer Science from the University of Sydney and a strong foundation in machine learning and data analysis, I am excited about the opportunity to contribute to your data-driven initiatives.

During my doctoral research, I developed advanced machine learning models and published multiple papers in reputable journals, showcasing my ability to translate complex data into actionable insights. My expertise in algorithms, statistical analysis, and programming has equipped me to tackle challenging data problems effectively. Additionally, my strong problem-solving and critical thinking skills enable me to approach complex challenges analytically and creatively.

I have hands-on experience with full-stack development, enabling me to build and deploy end-to-end data solutions. My strong experience with machine learning frameworks allows me to implement algorithms that drive business outcomes. Moreover, I thrive in collaborative environments, valuing teamwork as a crucial component of successful projects.

I am eager to apply my analytical skills, collaborative approach, and technical expertise to contribute to your team.

Thank you for taking the time to review my application. I look forward
to hopefully meeting with you in the future to further discuss my
qualifications. If you have any questions, please feel free to
email me at \href{mailto:tung6100@sydney.edu.au}{tung6100@sydney.edu.au} or
call me at \href{tel:0410935365}{0410935365}.

Sincerely,

\vspace{.15in}

Tung Anh

\end{document}