\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=Tung,
    middleinitial=Anh,
    lastname=Nguyen,
    email=tung6100@uni.sydney.edu.au,
    phone=0410935365,
    linkedin=tunganhnguyenusyd,
    % github=https://github.com/LeoTungAnh,
    city=Sydney,
    state=NSW,
    % qrcode=./images/qr.png,
    fixobjectivespacing=true
]

\objective{A data science enthusiast working on applied machine learning for solving real world problems.}

% ----- Education -----
\section{Education}

\experience{Electrical Engineering}{Bachelor of Science}{Aug 2011}{May 2016}{
    \noindent Top 5\% over 400 students \hfill GPA: 3.45/4.00 \newline
    Hanoi University of Science and Technology, Hanoi city, Viet Nam \newline
}

\experience{Machine Learning and Blockchain}{Master of Science}{Aug 2017}{Aug 2019}{
    \noindent Computer and Information Department \hfill GPA: 4.39/4.50 \newline
    Korea University, South Korea \newline
    Thesis title: Dynamic Data Aggregation in CoAP Based on Markov Chain for IoT Networks\newline
}

\experience{Machine Learning}{PhD}{Jul 2021}{Dec 2024}{
    \noindent School of Computer Science \newline
    University of Sydney, NSW, Australia \newline
    Thesis title: Resilient and Communication-Efficient Federated Learning for Scalable Heterogeneous IoT Data Modeling on Gassmann Manifolds.
}
% ----- Work Experience -----
\section{Professional Experience}

\experience{University of Sydney}{Teaching Assistant}{Jul 2021}{Present}{
\noindent Teaching, Tutoring, and Designing Course Content for:
    \achievement{
        Comp5318: Introduction to Machine Learning.
    }
    \achievement{
        Comp5348: Enterprise Scale Software Architecture.
    }
    \achievement{
        Comp9121: Design of Networks and Distributed Systems.
    }
    \achievement{
        Comp3221: Distributed Systems.
    }
}
\experience{University of Sydney}{AI Researcher}{Jul 2021}{Present}{
        \noindent Research Interests: Federated Learning, Distributed
        Optimization, Time Series Forecasting, Anomaly Detection, LLM.

    \noindent \textit{Highlighted Research}:
        \achievement{
            Proposed the world's first unsupervised federated learning algorithm, accepted at the A* conference INFOCOM 2023, titled:
            \textit{Federated PCA on grassmann manifold for anomaly detection in IoT networks.}
        }
        \achievement{
        Conducted large-scale experiments on thousands of IoT devices,
        applying algorithms to low-computation, privacy-conscious
        environments. Proved the convergence of the traditional ADMM
        algorithm under a sub-sampling scheme with rigorous theoretical
        support. This work has been accepted in a Q1 journal, titled:
            \textit{Federated PCA on Grassmann Manifold for IoT Anomaly Detection.}
        }

    \noindent \textit{"My PhD has equipped me with advanced critical thinking and problem-solving skills, enabling me to excel in teamwork and effectively build systems from scratch while enhancing existing solutions based on state-of-the-art research."}

}
\experience{Wilhelm Intergrated Solutions}{Data Analysis Intern}{Jun 2023}{Sept 2023}{
    \achievement{
        Provided strategic insights on cost and energy consumption in operating theaters adjacent to high-risk areas, contributing to improved resource allocation and operational efficiency.
    }
    \achievement{
        Conducted causal analysis and hypothesis testing to identify key factors influencing patient infection rates, driving actionable changes in hospital protocols.
    }
    \achievement{
        Designed and implemented a data collection protocol for operating theaters, including comprehensive tracking of patient outcomes post-surgery, ensuring data accuracy for quality improvement.
    }
    \achievement{
        Developed an automated notification system that alerts staff to unusual conditions in operating theaters via Slack, enhancing response times and safety.
    }
    \achievement{
        Built an automated data analysis system that generates real-time reports on daily, weekly, and monthly data, streamlining decision-making processes.
    }
}
\experience{IVIRSE(a healthcare start up company)}{AI Engineer}{Jul 2021}{Jul 2023}{
    \achievement{
        Designed and implemented an end-to-end machine learning pipeline, encompassing data preprocessing, model training, and deployment, significantly improving workflow efficiency.
    }
    \achievement{
    Developed and deployed CI/CD pipelines for machine learning model
    training and production models on AWS, streamlining automation and reducing
    deployment time.
    }
    \achievement{
        Built an LLM-powered chatbot that effectively replaced the customer service team in handling patient inquiries, improving response time and operational efficiency.
    }
    \achievement{
        Created an LLM-based doctor assistant for document summarization and information retrieval, enabling faster decision-making and patient care by doctors.
    }
    \achievement{
        Constructed a Hadoop-based datalake and utilized Spark to process and query data, reducing pipeline processing time by 1.75x compared to traditional relational databases.
    }
}

\experience{Viettel R \& D}{Embedded Software Team Leader}{Sept 2019}{Jun 2021}{
    \achievement{
    Developed advanced machine learning algorithms for 5G chip embedded
    systems for enhancing signal processing
    capabilities of Digital Predistortion block.
    }
    \achievement{
    Development of algorithms optimized for a customized CPU, enabling
    advanced control and processing of telecommunication signals. Led
    the world-first integration of Xilinx and ADI 5G systems into a
    customized CPU architecture.
    }
}
\experience{IBM and Linux Foundation}{Software Engineer Intern}{Aug 2016}{Jul 2017}{
    \achievement{
    Designed and implemented a blockchain system for Industrial
    IoT (IIoT) utilizing Hyperledger Fabric and Docker Compose.
    Recognized as one of the most successful projects in the internship
    program. The system enables  tracking of construction
    activities and securely records data on the blockchain. The collected data is analyzed and reported to project administrators, enhancing project oversight and decision-making.    }
}
\experience{HUMAX R\&D}{Software Engineer}{Aug 2016}{Jul 2017}{
    \achievement{
        Developed firmware for operating systems in microcontrollers, enhancing system functionality and performance through efficient code optimization and hardware integration.
    }
}

\experience{Pohang University}{Machine Learning Intern}{Jan 2016}{Feb 2016}{
    \achievement{
    Developed a Convolutional Neural Network (CNN) on FPGA for image
    classification, optimizing performance and efficiency, and significantly advancing capabilities in real-time image processing applications.
    }
}
\section{Skills}
\achievement{
    \textbf{Programming Language}: Python, Pytorch, SQL, Javascript, Html, Css, C, C++.
}

\achievement{
    \textbf{Software Development}: Proficient in full-stack development
    with a strong coding background in data structures and algorithms,
    capable of designing and implementing end-to-end solutions.
}

\achievement{
    \textbf{Machine Learning}: Light weight and efficient Machine Learning for Networking with Federated Learning, Computer Vision, Time Series Prediction, Natural Language Processing,  Data Analysis, Hypothesis Testing, Data cleaning and Data preprocessing.
}

\achievement{
    \textbf{Database}: MongoDB, MySQL, Hadoop, Spark.
}

\achievement{
    \textbf{Cloud}: AWS, physical server.
}
\achievement{
    \textbf{Devops}: Docker, Jenkins, SonarQube, Kubernetes, ArgoCD.
}
\achievement{
    \textbf{MLOps}: WandB, MLflow, DVC, CML.
}

% ----- Awards and Recognitions -----
\section{Awards and Recognitions}
\experience{University of Sydney}{Faculty of Engineering Scholarship}{Jul 2021}{Present}{
}
\experience{Korea University}{Computer and Information Department Scholarship}{Jul 2017}{Aug 2019}{
}
\experience{Hanoi University of Science and Technology}{Best Student
Award}{2012}{2013}{ Awarded for having the highest academic record among
Bachelor’s students in the School of Electrical Engineering.
}

\experience{Hanoi University of Science and Technology}{Best Student
Award}{2013}{2014}{ Awarded for having the highest academic record among
Bachelor’s students in the School of Electrical Engineering.
}

\section{selected publications}
\begin{enumerate}
    \item Nguyen Tung-Anh, Jiayu He, Long Tan Le, Wei Bao, and Nguyen H. Tran. "Federated PCA on Grassmann Manifold for Anomaly Detection in IoT Networks." arXiv preprint arXiv:2212.12121 (2022), INFOCOM2023.
    \item Nguyen Tung-Anh, et al. "Federated PCA on Grassmann Manifold for IoT Anomaly Detection." IEEE/ACM Transactions on Networking (2024).
    \item Nguyen Tung-Anh, Tuan Dung Nguyen, Long Tan Le, Canh T. Dinh, and Nguyen H. Tran. "On the Generalization of Wasserstein Robust Federated Learning." arXiv preprint arXiv:2206.01432 (2022).
    \item He J, Khushi M, Nguyen TA, Tran NH. Fed-mSSA: A Federated Approach for Spatio-Temporal Data Modeling Using Multivariate Singular Spectrum Analysis. In2023 IEEE International Conference on Data Mining (ICDM) 2023 Dec 1 (pp. 1055-1060). IEEE.
\end{enumerate}
\section{references}

\achievement{
    \textbf{Associate Professor Nguyen. H Tran}

    School of Computer Science in University of Sydney

    Rm 428, J12 Building, The University of Sydney, 1 Cleveland Street, Darlington, NSW 2006, Australia

    \emph{nguyen.tran@sydney.edu.au}
}

\end{document}